### 2019-02-26 sections/example.tex
call editor an editor

The function \TS{confirmBooking} removes the picked seats from the shared list of free seats,
and displays the end result using the \TS{edit}-construct.\fixme{Alejandro: Give \TS{edit} a proper name?}
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.

>>>>

The function \TS{confirmBooking} removes the picked seats from the shared list of free seats,
and displays the end result using an editor \TS{edit}.
\begin{TASK}
  let confirmBooking = \ps. \ss.
    freeSeats := difference !freeSeats ss; edit <<ps, ss>>
\end{TASK}
% It uses a function \TS{difference}, which removes all elements from the second list from the first list.
